---
title: "20211213_ChIRPKitRep1_Firre_RTqPCR"
output: html_document
editor_options: 
  chunk_output_type: console
---



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, warning=FALSE)
library(tidyverse)
library(readxl)
library(ggplot2)
```

ChIRP Pulldown of Firre Compared to Input

```{r computed level}
results_Firre <- read_excel("20211213_ChIRPKit_Firre_fix.xlsx",
           sheet="ANOVA Work",
           range="i1:j7",
           col_names=TRUE,
           trim_ws=TRUE)
results_NegControls <- read_excel("20211213_ChIRPKit_Firre_fix.xlsx",
           sheet="ANOVA Work",
           range="k1:l13",
           col_names=TRUE,
           trim_ws=TRUE)
results_Odd <- read_excel("20211213_ChIRPKit_Firre_fix.xlsx",
           sheet="ANOVA Work",
           range="b1:c10",
           col_names=TRUE,
           trim_ws=TRUE)
results_Even <- read_excel("20211213_ChIRPKit_Firre_fix.xlsx",
           sheet="ANOVA Work",
           range="e1:f10",
           col_names=TRUE,
           trim_ws=TRUE)
data_odd_even <- read_excel("20211213_ChIRPKit_Firre_fix.xlsx",
           sheet="ANOVA Work",
           range="o1:q10",
           col_names=TRUE,
           trim_ws=TRUE)
data_transcripts <- read_excel("20211213_ChIRPKit_Firre_fix.xlsx",
           sheet="ANOVA Work",
           range="s1:v7",
           col_names=TRUE,
           trim_ws=TRUE)
```
One-Way Anova to Test Significance between Transcripts

Research Question : Is Firre pulldown significant compared to negaive control transcripts in ChIRP experiments with WT mES Cells using RT-qPCR data? 

```{r}
Odd_Firre_v_Gapdh.aov <- aov(Odd ~ Sample, data=results_Odd[1:6,])
summary(Odd_Firre_v_Gapdh.aov)

Odd_Firre_v_mTug1.aov <- aov(Odd ~ Sample, data=results_Odd[4:9,])
summary(Odd_Firre_v_mTug1.aov)

Even_Firre_v_Gapdh.aov <- aov(Even ~ Sample, data=results_Even[1:6,])
summary(Even_Firre_v_Gapdh.aov)

Even_Firre_v_mTug1.aov <- aov(Even ~ Sample, data=results_Even[4:9,])
summary(Even_Firre_v_mTug1.aov)
```

Two ANOVA to Test Significance between Transcripts for WT mES Cells by tying together both odd and even oligo sets
Expectation: No difference between Odd and Even Sets, but might get some, especially for Firre

```{r}
print("Odd and Even Multivariable ANOVA")
Odd_Even_results.man <- manova(cbind(Firre, mTUG1, Gapdh) ~ Sample, data = data_transcripts)
summary(Odd_Even_results.man)
summary.aov(Odd_Even_results.man)
```


