---
title: "2022_03_14_Wilcoxon_RankSum_Test_Jan2022_KitJan2022TV"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rstatix)
library(ggpubr)
library(dplyr)
library(purrr)
library(janitor)
knitr::opts_chunk$set(echo = TRUE)
```

##Purpose = Perform Wilcoxon Rank Sum Test on both Spectral Data and Intensities for the two data sets
##Then compare the significant finds in a venn diagram
#More helpful info on Wilcoxon Rank Sum Test from UVA
#https://data.library.virginia.edu/the-wilcoxon-rank-sum-test/

#Making Tibbles of Spectral data for each protein from the Jan2022FA and Jan2022TVkit data
```{r}

#Jan2022FA data
mass_spec_Jan2022_FA <- read_csv("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis/20220107_SCP_FAriel.csv")
#Clean up column names
#colnames(mass_spec_Jan2022_FA) <- paste(colnames(mass_spec_Jan2022_FA),"Jan2022FA",sep="_")
#Making tibbles from KO and WT spectral counts from the data
KO_spectral_mass_spec_Jan2022_FA <- mass_spec_Jan2022_FA[,c(4,13,15,17,19,21,23,25,27)]
WT_spectral_mass_spec_Jan2022_FA <- mass_spec_Jan2022_FA[,c(4,29,31,33,35,37,39,41,43)]

#Jan2022TVkit Data Same thing. 
kit_mass_spec_Jan2022_TV <- read_csv("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis/2022_01_31_SCP_TVallery_combined_proteins.csv")
#colnames(kit_mass_spec_Jan2022_TV) <- paste(colnames(kit_mass_spec_Jan2022_TV),"KitJan2022TV",sep="_")
KO_spectral_mass_spec_Jan2022_TV <- kit_mass_spec_Jan2022_TV[,c(4,13,14)]
WT_spectral_mass_spec_Jan2022_TV <- kit_mass_spec_Jan2022_TV[,c(4,15,16)]

```

#Making Tibbles of Calculated Intensities for each dbp from the Jan2022FA and Jan2022TV data
```{r}
#Jan2022FA data
KO_intensities_mass_spec_Jan2022_FA <- mass_spec_Jan2022_FA[,c(4,14,16,18,20,22,24,26,28)]
WT_intensities_mass_spec_Jan2022_FA <- mass_spec_Jan2022_FA[,c(4,30,32,34,36,38,40,42,44)]

#Jan2022TVkit Data Same thing. 
KO_intensities_mass_spec_Jan2022_TV <- kit_mass_spec_Jan2022_TV[,c(4,17,18)]
WT_intensities_mass_spec_Jan2022_TV <- kit_mass_spec_Jan2022_TV[,c(4,19,20)]

```

#Full outer join by protein name, still keeping KO and WT separate
#Followed by some cleanup

```{r}
#For Spectral
KO_spectral=KO_spectral_mass_spec_Jan2022_TV %>% full_join(KO_spectral_mass_spec_Jan2022_FA,by="Gene")
WT_spectral=WT_spectral_mass_spec_Jan2022_TV %>% full_join(WT_spectral_mass_spec_Jan2022_FA,by="Gene")

#For Intensities
KO_intensities = KO_intensities_mass_spec_Jan2022_TV %>% full_join(KO_intensities_mass_spec_Jan2022_FA,by="Gene")
WT_intensities = WT_intensities_mass_spec_Jan2022_TV %>% full_join(WT_intensities_mass_spec_Jan2022_FA,by="Gene")

#Cleanup by making the Gene column a character column and N/A's into Zeros
KO_spectral <- as.data.frame(KO_spectral)
KO_spectral <- replace(KO_spectral, is.na(KO_spectral), 0)
WT_spectral <- as.data.frame(WT_spectral)
WT_spectral <- replace(WT_spectral, is.na(WT_spectral), 0)
KO_intensities <-as.data.frame(KO_intensities)
KO_intensities <- replace(KO_intensities, is.na(KO_intensities), 0)
WT_intensities <- as.data.frame(WT_intensities)
WT_intensities <- replace(WT_intensities, is.na(WT_intensities), 0)

#Spectral Clean up
KO_spectral <- KO_spectral[-c(280,297:305),]
KO_spectral <- KO_spectral[order(KO_spectral$Gene),]
WT_spectral <- WT_spectral[-c(280,297:305),]
WT_spectral <- WT_spectral[order(WT_spectral$Gene),]
Spectral = WT_spectral %>% full_join(KO_spectral,by="Gene")
Spectral <- as.data.frame(t(Spectral))
Spectral_newcol <- c("Genotype","WT","WT","WT","WT","WT","WT","WT","WT","WT","WT","KO","KO","KO","KO","KO","KO","KO","KO","KO","KO")
Spectral <- cbind(Spectral_newcol,Spectral)
Spectral <- Spectral %>% row_to_names (row_number= 1) %>% clean_names()
Spectral[] <- lapply(Spectral, type.convert, as.is = TRUE)

#Intensities Clean up
KO_intensities <- KO_intensities[-c(280,297:305),]
KO_intensities <- KO_intensities[order(KO_intensities$Gene),]
WT_intensities <- WT_intensities[-c(280,297:305),]
WT_intensities <- WT_intensities[order(WT_intensities$Gene),]
Intensities = WT_intensities %>% full_join(KO_intensities,by="Gene")
Intensities <- as.data.frame(t(Intensities))
Intensities_newcol <- c("Gene","WT","WT","WT","WT","WT","WT","WT","WT","WT","WT","KO","KO","KO","KO","KO","KO","KO","KO","KO","KO")
Intensities <- cbind(Intensities_newcol,Intensities)
Intensities <-Intensities %>% row_to_names (row_number= 1) %>% clean_names()
Intensities[] <- lapply(Intensities, type.convert, as.is = TRUE)

```

```{r}
typeof(Spectral$aars1)
typeof(Intensities$aars1)
```


#Wilcoxon Test on Spectral
```{r}

test.fun <- function(Spectral, col) { 

 c1 <- combn(unique(Spectral$genotype),2)
 sigs <- list()
 for(i in 1:ncol(c1)) {
    sigs[[i]] <- wilcox.test(
                   Spectral[Spectral$genotype == c1[1,i],col],
                   Spectral[Spectral$genotype == c1[2,i],col], exact=FALSE
                 )
    }
    names(sigs) <- paste("Group",c1[1,],"by Group",c1[2,])

 tests_Spectral <- data.frame(Test=names(sigs),
                    W=unlist(lapply(sigs,function(x) x$statistic)),
                    p=unlist(lapply(sigs,function(x) x$p.value)),row.names=NULL)

 return(tests_Spectral)
}


tests_Spectral <- lapply(colnames(Spectral)[-1],function(x) test.fun(Spectral,x))
names(tests_Spectral) <- colnames(Spectral)[-1]
# tests <- do.call(rbind, tests) reprints as data.frame



#KO_list = split(KO_spectral, f = KO_spectral$Gene)

```

#Wilcoxon Test on Intensities
```{r}

test.fun2 <- function(Intensities, col) { 

 c2 <- combn(unique(Intensities$gene),2)
 sigs2 <- list()
 for(i in 1:ncol(c2)) {
    sigs2[[i]] <- wilcox.test(
                   Intensities[Intensities$gene == c2[1,i],col],
                   Intensities[Intensities$gene == c2[2,i],col], exact=FALSE
                 )
    }
    names(sigs2) <- paste("Group",c2[1,],"by Group",c2[2,])

 tests_Intensities <- data.frame(Test=names(sigs2),
                    W=unlist(lapply(sigs2,function(x) x$statistic)),
                    p=unlist(lapply(sigs2,function(x) x$p.value)),row.names=NULL)

 return(tests_Intensities)
}


tests_Intensities <- lapply(colnames(Intensities)[-1],function(x) test.fun2(Intensities,x))
names(tests_Intensities) <- colnames(Intensities)[-1]
# tests <- do.call(rbind, tests) reprints as data.frame


#KO_list = split(KO_spectral, f = KO_spectral$Gene)

```


```{r}
results_Spectral <- do.call(rbind.data.frame, tests_Spectral)
write.csv(results_Spectral,"/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//results_Spectral.csv",row.names = FALSE)
results_Intensities <- do.call(rbind.data.frame, tests_Intensities)
write.csv(results_Intensities,"/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//results_Intensities.csv",row.names = FALSE)
```

