---
title: "2022_03_14_Wilcoxon_RankSum_Test_Jan2022_KitJan2022TV"
output: html_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(rstatix)
library(ggpubr)
library(dplyr)
library(purrr)
library(janitor)
library(ggplot2)
library(ggvenn)
library(VennDiagram)
library(venneuler)
library(eulerr)
library(reshape)
knitr::opts_chunk$set(echo = TRUE)
```

##Purpose = Perform Wilcoxon Rank Sum Test on both Spectral Data and Intensities for the two data sets
##Then compare the significant finds in a venn diagram
#More helpful info on Wilcoxon Rank Sum Test from UVA
#https://data.library.virginia.edu/the-wilcoxon-rank-sum-test/

#Making Tibbles of Spectral data for each protein from the Jan2022FA and Jan2022TVkit data
```{r}

#Jan2022FA data
mass_spec_Jan2022_FA <- read_csv("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis/20220107_SCP_FAriel.csv")
#Clean up column names
#colnames(mass_spec_Jan2022_FA) <- paste(colnames(mass_spec_Jan2022_FA),"Jan2022FA",sep="_")
#Making tibbles from KO and WT spectral counts from the data

#Below is grabbing the KO and WT separately. I will recombine these later but first I want to put the different datasets together. 
KO_spectral_mass_spec_Jan2022_FA <- mass_spec_Jan2022_FA[,c(4,13,15,17,19,21,23,25,27)]
WT_spectral_mass_spec_Jan2022_FA <- mass_spec_Jan2022_FA[,c(4,29,31,33,35,37,39,41,43)]

#Jan2022TVkit Data Same thing. 
kit_mass_spec_Jan2022_TV <- read_csv("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis/2022_01_31_SCP_TVallery_combined_proteins.csv")
#colnames(kit_mass_spec_Jan2022_TV) <- paste(colnames(kit_mass_spec_Jan2022_TV),"KitJan2022TV",sep="_")
KO_spectral_mass_spec_Jan2022_TV <- kit_mass_spec_Jan2022_TV[,c(4,13,14)]
WT_spectral_mass_spec_Jan2022_TV <- kit_mass_spec_Jan2022_TV[,c(4,15,16)]

```

#Making Tibbles of Calculated Intensities for each dbp from the Jan2022FA and Jan2022TV data
```{r}
#Jan2022FA data
KO_intensities_mass_spec_Jan2022_FA <- mass_spec_Jan2022_FA[,c(4,14,16,18,20,22,24,26,28)]
WT_intensities_mass_spec_Jan2022_FA <- mass_spec_Jan2022_FA[,c(4,30,32,34,36,38,40,42,44)]

#Jan2022TVkit Data Same thing. 
KO_intensities_mass_spec_Jan2022_TV <- kit_mass_spec_Jan2022_TV[,c(4,17,18)]
WT_intensities_mass_spec_Jan2022_TV <- kit_mass_spec_Jan2022_TV[,c(4,19,20)]

```

#Full outer join by protein name, still keeping KO and WT separate
#Followed by some cleanup

```{r}
#For Spectral
KO_spectral=KO_spectral_mass_spec_Jan2022_TV %>% full_join(KO_spectral_mass_spec_Jan2022_FA,by="Gene")
WT_spectral=WT_spectral_mass_spec_Jan2022_TV %>% full_join(WT_spectral_mass_spec_Jan2022_FA,by="Gene")

#For Intensities
KO_intensities = KO_intensities_mass_spec_Jan2022_TV %>% full_join(KO_intensities_mass_spec_Jan2022_FA,by="Gene")
WT_intensities = WT_intensities_mass_spec_Jan2022_TV %>% full_join(WT_intensities_mass_spec_Jan2022_FA,by="Gene")

#Cleanup by making the Gene column a character column and N/A's into Zeros
KO_spectral <- as.data.frame(KO_spectral)
KO_spectral <- replace(KO_spectral, is.na(KO_spectral), 0)
WT_spectral <- as.data.frame(WT_spectral)
WT_spectral <- replace(WT_spectral, is.na(WT_spectral), 0)
KO_intensities <-as.data.frame(KO_intensities)
KO_intensities <- replace(KO_intensities, is.na(KO_intensities), 0)
WT_intensities <- as.data.frame(WT_intensities)
WT_intensities <- replace(WT_intensities, is.na(WT_intensities), 0)

#Spectral Clean up
KO_spectral <- KO_spectral[-c(280,297:305),]
KO_spectral <- KO_spectral[order(KO_spectral$Gene),]
WT_spectral <- WT_spectral[-c(280,297:305),]
WT_spectral <- WT_spectral[order(WT_spectral$Gene),]
Spectral = WT_spectral %>% full_join(KO_spectral,by="Gene")
Spectral <- as.data.frame(t(Spectral))
Spectral_newcol <- c("Genotype","WT","WT","WT","WT","WT","WT","WT","WT","WT","WT","KO","KO","KO","KO","KO","KO","KO","KO","KO","KO")
Spectral <- cbind(Spectral_newcol,Spectral)
Spectral <- Spectral %>% row_to_names (row_number= 1) %>% clean_names()
Spectral[] <- lapply(Spectral, type.convert, as.is = TRUE)

#Intensities Clean up
KO_intensities <- KO_intensities[-c(280,297:305),]
KO_intensities <- KO_intensities[order(KO_intensities$Gene),]
WT_intensities <- WT_intensities[-c(280,297:305),]
WT_intensities <- WT_intensities[order(WT_intensities$Gene),]
Intensities = WT_intensities %>% full_join(KO_intensities,by="Gene")
Intensities <- as.data.frame(t(Intensities))
Intensities_newcol <- c("Gene","WT","WT","WT","WT","WT","WT","WT","WT","WT","WT","KO","KO","KO","KO","KO","KO","KO","KO","KO","KO")
Intensities <- cbind(Intensities_newcol,Intensities)
Intensities <-Intensities %>% row_to_names (row_number= 1) %>% clean_names()
Intensities[] <- lapply(Intensities, type.convert, as.is = TRUE)

```

```{r}
typeof(Spectral$aars1)
typeof(Intensities$aars1)
```


#Wilcoxon Test on Spectral. 
#Output is a csv file to have the pvalues in a table format. 
```{r}

test.fun <- function(Spectral, col) { 

 c1 <- combn(unique(Spectral$genotype),2)
 sigs <- list()
 for(i in 1:ncol(c1)) {
    sigs[[i]] <- wilcox.test(
                   Spectral[Spectral$genotype == c1[1,i],col],
                   Spectral[Spectral$genotype == c1[2,i],col], exact=FALSE
                 )
    }
    names(sigs) <- paste("Group",c1[1,],"by Group",c1[2,])

 tests_Spectral <- data.frame(Test=names(sigs),
                    W=unlist(lapply(sigs,function(x) x$statistic)),
                    p=unlist(lapply(sigs,function(x) x$p.value)),row.names=NULL)

 return(tests_Spectral)
}


tests_Spectral <- lapply(colnames(Spectral)[-1],function(x) test.fun(Spectral,x))
names(tests_Spectral) <- colnames(Spectral)[-1]
# tests <- do.call(rbind, tests) reprints as data.frame



#KO_list = split(KO_spectral, f = KO_spectral$Gene)

```

#Wilcoxon Test on Intensities
#Output is a csv file to have the pvalues in a table format. 
```{r}

test.fun2 <- function(Intensities, col) { 

 c2 <- combn(unique(Intensities$gene),2)
 sigs2 <- list()
 for(i in 1:ncol(c2)) {
    sigs2[[i]] <- wilcox.test(
                   Intensities[Intensities$gene == c2[1,i],col],
                   Intensities[Intensities$gene == c2[2,i],col], exact=FALSE
                 )
    }
    names(sigs2) <- paste("Group",c2[1,],"by Group",c2[2,])

 tests_Intensities <- data.frame(Test=names(sigs2),
                    W=unlist(lapply(sigs2,function(x) x$statistic)),
                    p=unlist(lapply(sigs2,function(x) x$p.value)),row.names=NULL)

 return(tests_Intensities)
}


tests_Intensities <- lapply(colnames(Intensities)[-1],function(x) test.fun2(Intensities,x))
names(tests_Intensities) <- colnames(Intensities)[-1]
# tests <- do.call(rbind, tests) reprints as data.frame


#KO_list = split(KO_spectral, f = KO_spectral$Gene)

```

#Writing CSV of the Wilcoxon Test
```{r}
results_Spectral <- do.call(rbind.data.frame, tests_Spectral)
write.csv(results_Spectral,"/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//results_Spectral.csv",row.names = FALSE)
results_Intensities <- do.call(rbind.data.frame, tests_Intensities)
write.csv(results_Intensities,"/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//results_Intensities.csv",row.names = FALSE)
```

#Histogram of p-values
```{r}
hist(results_Spectral$p, breaks = 20, main="Frequency of Wilcoxon Rank Sum Test P-values \nComparing KO with WT Mass Spec Spectral Counts from FAJan2022 and TVkitJan2022", xlab = "P-value from Wilcoxon Rank Sum Test", ylab = "Frequency of Genes", labels=TRUE) 

# saving the figure (we will do this over and over again :)
# we will learn ggplot later but we use PDF and turn of null device (plot window) 

pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_15_Histogram_Wilcoxon_Spectral_MassSpec_Jan2022FA_v_Jan2022TV.pdf")
hist(results_Spectral$p, breaks = 20, main="Frequency of Wilcoxon Rank Sum Test P-values \nComparing KO with WT Mass Spec Spectral Countsfrom FAJan2022 and TVkitJan2022", xlab = "P-value from Wilcoxon Rank Sum Test", ylab = "Frequency of Genes", labels=TRUE) 
dev.off()

#intensities
hist(results_Intensities$p, breaks = 20, main="Frequency of Wilcoxon Rank Sum Test P-values \nComparing KO with WT Mass Spec Intensities from FAJan2022 and TVkitJan2022", xlab = "P-value from Wilcoxon Rank Sum Test", ylab = "Frequency of Genes", labels=TRUE) 

pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_15_Histogram_Wilcoxon_Intensities_MassSpec_Jan2022FA_v_Jan2022TV.pdf")
hist(results_Intensities$p, breaks = 20, main="Frequency of Wilcoxon Rank Sum Test P-values \nComparing KO with WT Mass Spec Intensities from FAJan2022 and TVkitJan2022", xlab = "P-value from Wilcoxon Rank Sum Test", ylab = "Frequency of Genes", labels=TRUE) 
dev.off()

```
#Genes Below 0.05 and 0.10 p-value
#Feel free to change the names and the pvalue cutoffs
```{r}
results_Spectral <- results_Spectral %>% 
  mutate(significance = ifelse(p < 0.05, "very",
                          ifelse(p < 0.10, "significant", "not")))

significant <- c("very", "significant")
pattern_to_search <- paste0(significant, collapse = "|")

significantSpectral_genes <- results_Spectral[grepl(pattern_to_search, results_Spectral$significance), ]

results_Intensities <- results_Intensities%>% 
  mutate(significance = ifelse(p < 0.05, "very",
                          ifelse(p < 0.10, "significant", "not")))

significantIntensities_genes <- results_Intensities[grepl(pattern_to_search, results_Intensities$significance), ]

```

#Venn diagram of genes that are significant in Intensities and Spectral Counts
#Dataframes of common (found as significant in both Intensities and Spectral counts)
#Feel free to silence this one. I used this for my initial analysis. 
```{r}
significantSpectral_genes$gene <- row.names(significantSpectral_genes)
typeof(significantSpectral_genes$gene)
significantIntensities_genes$gene <- row.names(significantIntensities_genes)
genes <- list(MassSpecSpectral = sort(significantSpectral_genes$gene), MassSpecIntensities = sort(significantIntensities_genes$gene))
pdf("2022_03_15_VennDiagram_MassSpec_SignificantGeneOverlap.pdf")
ggvenn(genes, c("MassSpecSpectral", "MassSpecIntensities"))
dev.off()


venn_win <- euler(c(Spectral=29, Intensities=23, "Spectral&Intensities"=9), shape = "ellipse")
pdf("2022_03_15_VennDiagram_MassSpec_SignificantGeneOverlap_bysize.pdf")
plot(venn_win, fill = c("white", "lightcoral"), quantities = list(fontsize = 13))
dev.off()

commongenes = merge(x=significantSpectral_genes,y=significantIntensities_genes,by="gene")
commongenes
write.csv(commongenes, file = "2022_03_15_commongenes.csv", row.names=TRUE)
allgenes = merge(x=significantSpectral_genes,y=significantIntensities_genes,by="gene",all=TRUE)
allgenes
write.csv(allgenes, file = "2022_03_15_allgenes.csv", row.names=TRUE)
```

#Box-whisker plots of common genes to check that I believe the significance
#Feel free to silence. This was just a quality control. 
#You'll find that I have a big box-whisker plot of common gene, KO vs. WT, for both
#intensities and spectral plots. This is saved as a pdf.
#The For Loop generates individual box-whisker plots for each common gene and puts them in a folder. 
#So make folders ahead of time. 
#You'll find that I melt the data. This is essential for getting the box whisker plot to work.
```{r}
#Common genes Spectral
#pattern_to_search_commongenes <- paste0(commongenes$gene, collapse = "|")
#long_data_Spectral_sig_commongenes <- Spectral[, grep(pattern_to_search_commongenes, colnames(Spectral))]
#genotype <- c("WT","WT","WT","WT","WT","WT","WT","WT","WT","WT","KO","KO","KO","KO","KO","KO","KO","KO","KO","KO")
#long_data_Spectral_sig_commongenes <- cbind(genotype,long_data_Spectral_sig_commongenes)
#mm_commonSpectral = melt(long_data_Spectral_sig_commongenes)


#pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_16_commongenes_Spectral_boxwhisker_Wilcoxon_S_MassSpec_Jan2022FA_v_Jan2022TV.pdf")
#ggplot(mm_commonSpectral,fill = "#00AFBB")+geom_boxplot(aes(x=genotype, y=value))+facet_grid(.~variable)
#dev.off()


#for (var in mm_commonSpectral$variable) { 
 
  #pdf(paste("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis/2022_03_16_MassSpec_SpectralBoxPlots_SignificantGenes//", var, ".pdf", sep=""))
  #print(ggplot(mm_commonSpectral[mm_commonSpectral$variable==var,],fill = "#00AFBB")+geom_boxplot(aes(x=genotype, y=value))+ggtitle(var))
  #dev.off()
  #}

#Common genes Intensities
#long_data_Intensities_sig_commongenes <- Intensities[, grep(pattern_to_search_commongenes, colnames(Intensities))]
#long_data_Intensities_sig_commongenes <- cbind(genotype,long_data_Intensities_sig_commongenes)
#mm_commonIntensities = melt(long_data_Intensities_sig_commongenes)


#pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_16_commongenes_Intensities_boxwhisker_Wilcoxon_S_MassSpec_Jan2022FA_v_Jan2022TV.pdf")
#ggplot(mm_commonIntensities)+geom_boxplot(aes(x=genotype, y=value))+facet_grid(.~variable)
#dev.off()


#for (var in mm_commonIntensities$variable) { 
 
  #pdf(paste("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis/2022_03_16_MassSpec_IntensitiesBoxPlots_SignificantGenes//", var, ".pdf", sep=""))
  #print(ggplot(mm_commonIntensities[mm_commonIntensities$variable==var,],fill = "#00AFBB")+geom_boxplot(aes(x=genotype, y=value))+ggtitle(var))
  #dev.off()
  #}

#https://stackoverflow.com/questions/26164676/ggplot-boxplot-for-multiple-columns-with-a-factor
#https://stackoverflow.com/questions/11346880/r-plot-multiple-box-plots-using-columns-from-data-frame

#significance


    
#stat.test <- long_data_Spectral_sig_allgenes %>%
# wilcox_test( aars1 ~ genotype) %>%
 #add_significance()
#stat.test

#report
#stat.test[i] <- stat.test[i] %>% add_xy_position(x = "genotype")
#bxp + 
 #stat_pvalue_manual(stat.test, tip.length = 0) +
 #labs(subtitle = get_test_label(stat.test, detailed= TRUE))
#}

```
#Same thing but now for Significant genes
#Pvalues are on individual graphs, but not the big graph. 
#Graphs here are fancy and pretty close to publication ready. 
#Feel free to change the fill color. It's teal. 
```{r}
#genes with pvalues <0.05. Making Box Whisker Plots, both all together and individual

#Spectral
#in the future I might have to grep these names
sig_genes <- c("anxa1","atp5f1a","btf3","ckb","hdlbp","hnrnpm","mif","naa15","pabpc1","pkp1","rpl10$","rpl38","slc25a5")
pattern_to_search_sig_genes <- paste0(sig_genes, collapse = "|")
long_data_Spectral_sig_genes <- Spectral[, grep(pattern_to_search_sig_genes, colnames(Spectral))]
genotype <- c("WT","WT","WT","WT","WT","WT","WT","WT","WT","WT","KO","KO","KO","KO","KO","KO","KO","KO","KO","KO")
long_data_Spectral_sig_genes <- cbind(genotype,long_data_Spectral_sig_genes)
mm_sigSpectral = melt(long_data_Spectral_sig_genes)

  pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_17_sig_genes_Spectral_boxwhisker_Wilcoxon_S_MassSpec_Jan2022FA_v_Jan2022TV.pdf")
  ggplot(mm_sigSpectral)+geom_boxplot(aes(x=genotype, y=value),fill = "#00AFBB")+facet_grid(.~variable)
  dev.off()


for (var in mm_sigSpectral$variable) { 
 
  pdf(paste("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis/2022_03_16_MassSpec_SpectralBoxPlots_SignificantGenes//", var, "_sig.pdf", sep=""))
  print(ggpaired(mm_sigSpectral[mm_sigSpectral$variable==var,],x="genotype",y="value",fill="#00AFBB",line.color ="gray")+ggtitle(var)+stat_compare_means(label.x = 0.5))
  dev.off()
  }

#Intensities
long_data_Intensities_sig_genes <- Intensities[, grep(pattern_to_search_sig_genes, colnames(Intensities))]
genotype <- c("WT","WT","WT","WT","WT","WT","WT","WT","WT","WT","KO","KO","KO","KO","KO","KO","KO","KO","KO","KO")
long_data_Intensities_sig_genes <- cbind(genotype,long_data_Intensities_sig_genes)
mm_sigIntensities = melt(long_data_Intensities_sig_genes)

pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_17_sig_genes_Intensities_boxwhisker_Wilcoxon_S_MassSpec_Jan2022FA_v_Jan2022TV.pdf")
ggplot(mm_sigIntensities)+geom_boxplot(aes(x=genotype, y=value),fill = "#00AFBB")+facet_grid(.~variable)
dev.off()

for (var in mm_sigIntensities$variable) { 
             
  pdf(paste("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis/2022_03_16_MassSpec_IntensitiesBoxPlots_SignificantGenes//", var, "_sig.pdf", sep=""))
  #print(ggplot(mm_sigIntensities[mm_sigIntensities$variable==var,])+geom_boxplot(aes(x=genotype, y=value),fill="#00AFBB")+ggtitle(var))
  print(ggpaired(mm_sigIntensities[mm_sigIntensities$variable==var,],x="genotype",y="value",fill="#00AFBB",line.color ="gray")+ggtitle(var)+stat_compare_means(label.x = 0.5))
  dev.off()
}

#Trying to add pvalues to plots.
#Help websites
#https://www.datanovia.com/en/blog/ggpubr-how-to-add-p-values-generated-elsewhere-to-a-ggplot/
#https://www.r-bloggers.com/2017/06/add-p-values-and-significance-levels-to-ggplots/
#http://www.sthda.com/english/articles/24-ggpubr-publication-ready-plots/76-add-p-values-and-significance-levels-to-ggplots/
```

#Histogram of all intensities 
#Calculating the mean of the 6 interesting genes for both spectral counts and intensities
#Saving the means in a csv file 
#Need to figure out how to incorporate the data from the table into the histogram. 
```{r}
#Spectral Counts
mm_allSpectral = melt(Spectral)
mm_allSpectral$logvalue=log(mm_allSpectral$value,10)
hist(mm_allSpectral$logvalue, breaks = 20, main="Histogram of Spectral Counts in Log Scale \nfrom Mass Spec Runs FAJan2022 and TVkitJan2022", xlab = "log(Spectral Counts)", ylab = "Frequency of Spectral Count Value", labels=TRUE) 

# saving the figure (we will do this over and over again :)
# we will learn ggplot later but we use PDF and turn of null device (plot window) 

pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_21_Histogram_Spectral_MassSpec_Jan2022FA_v_Jan2022TV.pdf")
hist(mm_allSpectral$logvalue, breaks = 20, main="Histogram of Spectral Counts in Log Scale\nfrom Mass Spec Runs FAJan2022 and TVkitJan2022", xlab = "Log(Spectral Counts)", ylab = "Frequency of Spectral Count Value", labels=TRUE) 
dev.off()


mean_spectral <- long_data_Spectral_sig_genes %>%
    group_by(genotype) %>% 
    summarise_each(funs(round(mean(.),2)))
#For entire column
#Spectral_sig_genes <- Spectral[, grep(pattern_to_search_sig_genes, colnames(Spectral))]
#mean_spectral <- rbind(Spectral_sig_genes, colMeans = colMeans(Spectral_sig_genes))
write.csv(mean_spectral,"/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_21_meanSpectral_siggenes.csv",row.names = TRUE)


#Intensities
mm_allIntensities = melt(Intensities)
mm_allIntensities$logvalue=log(mm_allIntensities$value,10)
hist(mm_allIntensities$logvalue, breaks = 20, main="Histogram of Intensities in Log Scale \nfrom Mass Spec Runs FAJan2022 and TVkitJan2022", xlab = "Log(Intensities)", ylab = "Frequency of Intensity Value",labels=TRUE) 

# saving the figure (we will do this over and over again :)
# we will learn ggplot later but we use PDF and turn of null device (plot window) 

pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_21_Histogram_Intensites_MassSpec_Jan2022FA_v_Jan2022TV.pdf")
hist(mm_allIntensities$logvalue, breaks = 20, main="Histogram of Intensities in Log Scale \nfrom Mass Spec Runs FAJan2022 and TVkitJan2022", xlab = "Log(Intensities)", ylab = "Frequency of Intensity Value",labels=TRUE) 
dev.off()

mean_intensities <- long_data_Intensities_sig_genes %>%
    group_by(genotype) %>% 
    summarise_each(funs(round(mean(.),2)))

#Intensities_sig_genes <- Intensities[, grep(pattern_to_search_sig_genes, colnames(Intensities))]
#mean_intensities <- rbind(Intensities_sig_genes, colMeans = colMeans(Intensities_sig_genes))
#keep in mind the above means are not in log scale. So you'll have to transform these in the table later. 
write.csv(mean_intensities,"/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_21_meanIntensities_siggenes.csv",row.names = TRUE)


```
#BoxWhisker Plots of the 6 Interesting Signficiant Genes ONLY
```{r}
sig_genes6 <- c("anxa1","btf3","hnrnpm","mif","naa15","rpl10$")
pattern_to_search_sig_genes6 <- paste0(sig_genes6, collapse = "|")

#Spectral Counts
long_data_Spectral_sig_genes6 <- Spectral[, grep(pattern_to_search_sig_genes6, colnames(Spectral))]
log_longdata_Spectral_sig_genes6 <- log(long_data_Spectral_sig_genes6,10)
genotype <- c("WT","WT","WT","WT","WT","WT","WT","WT","WT","WT","KO","KO","KO","KO","KO","KO","KO","KO","KO","KO")
long_data_Spectral_sig_genes6<- cbind(genotype,long_data_Spectral_sig_genes6)

mm_sigSpectral6 = melt(long_data_Spectral_sig_genes6)

  pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_22_6sig_genes_Spectral_boxwhisker_Wilcoxon_S_MassSpec_Jan2022FA_v_Jan2022TV.pdf")
  ggplot(mm_sigSpectral6)+geom_boxplot(aes(x=genotype, y=value),fill = "#00AFBB")+facet_grid(.~variable)+stat_compare_means(aes(x=genotype, y=value,group = genotype),label = "p.format", label.y = 4.5)
  #expression(atop("A long string of text for the purpose", paste("of illustrating my point" [reported])))
  #label.x = 0.5
  dev.off()

#logscale
#log_longdata_Spectral_sig_genes6 <- data.frame(lapply(log_longdata_Spectral_sig_genes6, function(x) {gsub("-Inf", 0, x)}))
#log_longdata_Spectral_sig_genes6[] <- lapply(log_longdata_Spectral_sig_genes6, type.convert, as.is = TRUE)
#log_longdata_Spectral_sig_genes6<- cbind(genotype,log_longdata_Spectral_sig_genes6)

#mm_logsigSpectral6 = melt(log_longdata_Spectral_sig_genes6)

  #pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_22_log6sig_genes_Spectral_boxwhisker_Wilcoxon_S_MassSpec_Jan2022FA_v_Jan2022TV.pdf")
  #ggplot(mm_logsigSpectral6)+geom_boxplot(aes(x=genotype, y=value),fill = "#00AFBB")+facet_grid(.~variable)+stat_compare_means(aes(x=genotype, y=value,group = genotype),label = "p.format", label.y = 0.75)
  #expression(atop("A long string of text for the purpose", paste("of illustrating my point" [reported])))
  #label.x = 0.5
 # dev.off()
  
#Intensities
sig_genes6 <- c("anxa1","btf3","hnrnpm","naa15","rpl10$")
long_data_Intensities_sig_genes6 <- Intensities[, grep(pattern_to_search_sig_genes6, colnames(Intensities))]
genotype <- c("WT","WT","WT","WT","WT","WT","WT","WT","WT","WT","KO","KO","KO","KO","KO","KO","KO","KO","KO","KO")
long_data_Intensities_sig_genes6 <- cbind(genotype,long_data_Intensities_sig_genes6)
mm_sigIntensities6 = melt(long_data_Intensities_sig_genes6)

pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_22_6sig_genes_Intensities_boxwhisker_Wilcoxon_S_MassSpec_Jan2022FA_v_Jan2022TV.pdf")
ggplot(mm_sigIntensities6)+geom_boxplot(aes(x=genotype, y=value),fill = "#00AFBB")+facet_grid(.~variable)+stat_compare_means(aes(x=genotype, y=value,group = genotype),label = "p.format")
dev.off()

#Sig Genes Minus RPL10 because not significant in intensities
sig_genes5 <- c("anxa1","btf3","hnrnpm","naa15")
pattern_to_search_sig_genes5 <- paste0(sig_genes5, collapse = "|")
long_data_Intensities_sig_genes5 <- Intensities[, grep(pattern_to_search_sig_genes5, colnames(Intensities))]
genotype <- c("WT","WT","WT","WT","WT","WT","WT","WT","WT","WT","KO","KO","KO","KO","KO","KO","KO","KO","KO","KO")
long_data_Intensities_sig_genes5 <- cbind(genotype,long_data_Intensities_sig_genes5)
mm_sigIntensities5 = melt(long_data_Intensities_sig_genes5)

#red fill below. Old Teal = "#00AFBB"
pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_02_01_FirreMassSpecData_Analysis//2022_03_22_4sig_genes_Intensities_boxwhisker_Wilcoxon_S_MassSpec_Jan2022FA_v_Jan2022TV.pdf")
ggplot(mm_sigIntensities5)+geom_boxplot(aes(x=genotype, y=value),fill = "#BB2526",size=0.5)+facet_grid(.~variable)+stat_compare_means(aes(x=genotype, y=value,group = genotype),label = "p.format")+ggtitle("Mass Spec Intensities of 4 Genes of Interest")+labs(y = "Mass Spec Intensity", x = "\nFirre Genotype in Mouse Embryonic Stem Cells")
dev.off()
##Hello

#Making a plot in red of the pulldown efficiency for odd and even probes

```

