---
title: "2022_03_28_Isabela_Firre_Gradients_F5_F6_WT_v_KO"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
library(tidyverse)
library(rstatix)
library(ggpubr)
library(dplyr)
library(purrr)
library(janitor)
library(ggplot2)
library(ggvenn)
library(VennDiagram)
library(venneuler)
library(eulerr)
library(reshape)
knitr::opts_chunk$set(echo = TRUE)
```

#Making Tibbles of Spectral data for each protein from the Jan2022FA and Jan2022TVkit data
```{r}

#50ng protein
#Anthony said the 50ng yielded more genes identified
mass_spec_50ng_Mar2022_SucGrad <- read_csv("/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_IsabelasGradientsFirreWTKO/2022_03_24_50ng_protein_SCP_JRinn_PTN_MESC_results.csv")
#Clean up column names
#colnames(mass_spec_Jan2022_FA) <- paste(colnames(mass_spec_Jan2022_FA),"Jan2022FA",sep="_")
#Making tibbles from KO and WT spectral counts from the data

#Below is grabbing the KO and WT separately. I will recombine these later but first I want to put the different datasets together. 
##Above is if you need to join data, we aren't so let's do all the same. 
Spectral_50ng <- mass_spec_50ng_Mar2022_SucGrad[,c(4,16,17,18,19)]
#WT_spectral_mass_spec_50ng_Mar2022_SucGrad <- mass_spec_50ng_Mar2022_SucGrad[,c(4,18,19)]

#100ng protein 
mass_spec_100ng_Mar2022_SucGrad <- read_csv("/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_IsabelasGradientsFirreWTKO/2022_03_24_100ng_protein_SCP_JRinn_PTN_MESC_results.csv")
#colnames(kit_mass_spec_Jan2022_TV) <- paste(colnames(kit_mass_spec_Jan2022_TV),"KitJan2022TV",sep="_")
Spectral_100ng <- mass_spec_100ng_Mar2022_SucGrad[,c(4,16,17,18,19)]
#WT_spectral_mass_spec_100ng_Mar2022_SucGrad <- mass_spec_100ng_Mar2022_SucGrad[,c(4,)]

```

#Making Tibbles of Calculated Intensities for each dbp from the Jan2022FA and Jan2022TV data
```{r}
#50 ng protein 
Intensities_50ng <- mass_spec_50ng_Mar2022_SucGrad[,c(4,28,29,30,31)]
#WT_intensities_mass_spec_50ng_Mar2022_SucGrad <- mass_spec_50ng_Mar2022_SucGrad[,c(4,30,31)]

#100ng protein same thing. 
Intensities_100ng <- mass_spec_100ng_Mar2022_SucGrad[,c(4,28,29,30,31)]
#WT_intensities_mass_spec_100ng_Mar2022_SucGrad <- mass_spec_100ng_Mar2022_SucGrad[,c(4,30,31)]

```

#Full outer join by protein name, still keeping KO and WT separate
#Followed by some cleanup

```{r}
#For Spectral
##Save this for later when I add in ChIRP results
#KO_spectral=KO_spectral_mass_spec_Jan2022_TV %>% full_join(KO_spectral_mass_spec_Mar2022_TV,by="Gene")
#WT_spectral=WT_spectral_mass_spec_Jan2022_TV %>% full_join(WT_spectral_mass_spec_Mar2022_TV,by="Gene")

#For Intensities
#KO_intensities = KO_intensities_mass_spec_Jan2022_TV %>% full_join(KO_intensities_mass_spec_Mar2022_TV,by="Gene")
#WT_intensities = WT_intensities_mass_spec_Jan2022_TV %>% full_join(WT_intensities_mass_spec_Mar2022_TV,by="Gene")

#Cleanup by making the Gene column a character column and N/A's into Zeros
#Needed only if I do a join
#KO_spectral <- as.data.frame(KO_spectral)
#KO_spectral <- replace(KO_spectral, is.na(KO_spectral), 0)
#WT_spectral <- as.data.frame(WT_spectral)
#WT_spectral <- replace(WT_spectral, is.na(WT_spectral), 0)
#KO_intensities <-as.data.frame(KO_intensities)
#KO_intensities <- replace(KO_intensities, is.na(KO_intensities), 0)
#WT_intensities <- as.data.frame(WT_intensities)
#WT_intensities <- replace(WT_intensities, is.na(WT_intensities), 0)

#Spectral Clean up
##Might have to check if these rows still need to be removed. 
#KO_spectral <- KO_spectral[-c(280,297:305),]
#KO_spectral <- KO_spectral_mass_spec_50ng_Mar2022_SucGrad[order(KO_spectral$Gene),]

#WT_spectral <- WT_spectral[-c(280,297:305),]
#WT_spectral <- WT_spectral[order(WT_spectral$Gene),]
#Spectral = WT_spectral %>% full_join(KO_spectral,by="Gene")
Spectral_50ng <- as.data.frame(t(Spectral_50ng))
Spectral_100ng <- as.data.frame(t(Spectral_100ng))
##Might have to check numbers of WT and KO to match below genotype cbind
Spectral_newcol <- c("Genotype","KO","KO","WT","WT")
Spectral_50ng <- cbind(Spectral_newcol,Spectral_50ng)
Spectral_100ng <- cbind(Spectral_newcol,Spectral_100ng)
Spectral_50ng <- Spectral_50ng %>% row_to_names (row_number= 1) %>% clean_names()
Spectral_100ng <- Spectral_100ng %>% row_to_names (row_number= 1) %>% clean_names()
Spectral_50ng[] <- lapply(Spectral_50ng, type.convert, as.is = TRUE)
Spectral_100ng[] <- lapply(Spectral_100ng, type.convert, as.is = TRUE)

#Intensities Clean up
##Same here check as you did in the above. 
#KO_intensities <- KO_intensities[-c(280,297:305),]
#KO_intensities <- KO_intensities[order(KO_intensities$Gene),]
#WT_intensities <- WT_intensities[-c(280,297:305),]
#WT_intensities <- WT_intensities[order(WT_intensities$Gene),]
#Intensities = WT_intensities %>% full_join(KO_intensities,by="Gene")
Intensities_50ng <- as.data.frame(t(Intensities_50ng))
Intensities_100ng <- as.data.frame(t(Intensities_100ng))
Intensities_newcol <- c("Gene","KO","KO","WT","WT")
Intensities_50ng <- cbind(Intensities_newcol,Intensities_50ng)
Intensities_50ng <-Intensities_50ng %>% row_to_names (row_number= 1) %>% clean_names()
Intensities_50ng[] <- lapply(Intensities_50ng, type.convert, as.is = TRUE)
Intensities_100ng <- cbind(Intensities_newcol,Intensities_100ng)
Intensities_100ng <-Intensities_100ng %>% row_to_names (row_number= 1) %>% clean_names()
Intensities_100ng[] <- lapply(Intensities_100ng, type.convert, as.is = TRUE)

```

##Need to change below gene to do a check. 
```{r}
typeof(Spectral_50ng$dhx8)
typeof(Spectral_100ng$dhx8)
typeof(Intensities_50ng$dhx8)
typeof(Intensities_100ng$dhx8)
```

#Making a Venn Diagram of the two datasets just to see overlap
##If this is interesting, go back to Feb 1st and grep the names to know common genes
```{r}
typeof(mass_spec_50ng_Mar2022_SucGrad$Gene)
genes <- list(SucGrad_50ng = sort(mass_spec_50ng_Mar2022_SucGrad$Gene), SucGrad_100ng = sort(mass_spec_100ng_Mar2022_SucGrad$Gene))
pdf("VennDiagram_MassSpec_GeneOverlap.pdf")
ggvenn(genes, c("SucGrad_50ng", "SucGrad_100ng"))
dev.off()

venn_win <- euler(c(Genes_50ng=628, Genes_100ng=473, "Genes_50ng&Genes_100ng"=3154), shape = "ellipse")
pdf("VennDiagram_MassSpec_GeneOverlap_bysize.pdf")
plot(venn_win, 
     fill = c("skyblue1", "lightcoral"),
     quantities = list(fontsize = 13))
dev.off()
```

#Wilcoxon Test on Spectral. 
#Output is a csv file to have the pvalues in a table format. 
```{r}

test.fun50 <- function(Spectral_50ng, col) { 

 c50 <- combn(unique(Spectral_50ng$genotype),2)
 sigs50 <- list()
 for(i in 1:ncol(c50)) {
    sigs50[[i]] <- wilcox.test(
                   Spectral_50ng[Spectral_50ng$genotype == c50[1,i],col],
                   Spectral_50ng[Spectral_50ng$genotype == c50[2,i],col], exact=FALSE
                 )
    }
    names(sigs50) <- paste("Group",c50[1,],"by Group",c50[2,])

 tests_Spectral_50 <- data.frame(Test=names(sigs50),
                    W=unlist(lapply(sigs50,function(x) x$statistic)),
                    p=unlist(lapply(sigs50,function(x) x$p.value)),row.names=NULL)

 return(tests_Spectral_50)
}


tests_Spectral_50ng <- lapply(colnames(Spectral_50ng)[-1],function(x) test.fun50(Spectral_50ng,x))
names(tests_Spectral_50ng) <- colnames(Spectral_50ng)[-1]
# tests <- do.call(rbind, tests) reprints as data.frame

test.fun100 <- function(Spectral_100ng, col) { 

 c100 <- combn(unique(Spectral_100ng$genotype),2)
 sigs100 <- list()
 for(i in 1:ncol(c100)) {
    sigs100[[i]] <- wilcox.test(
                   Spectral_100ng[Spectral_100ng$genotype == c100[1,i],col],
                   Spectral_100ng[Spectral_100ng$genotype == c100[2,i],col], exact=FALSE
                 )
    }
    names(sigs100) <- paste("Group",c100[1,],"by Group",c100[2,])

 tests_Spectral_100 <- data.frame(Test=names(sigs100),
                    W=unlist(lapply(sigs100,function(x) x$statistic)),
                    p=unlist(lapply(sigs100,function(x) x$p.value)),row.names=NULL)

 return(tests_Spectral_100)
}


tests_Spectral_100ng <- lapply(colnames(Spectral_100ng)[-1],function(x) test.fun100(Spectral_100ng,x))
names(tests_Spectral_100ng) <- colnames(Spectral_100ng)[-1]

#KO_list = split(KO_spectral, f = KO_spectral$Gene)

```

#Wilcoxon Test on Intensities
#Output is a csv file to have the pvalues in a table format. 
```{r}

test.funi50 <- function(Intensities_50ng, col) { 

 ci50 <- combn(unique(Intensities_50ng$gene),2)
 sigsi50 <- list()
 for(i in 1:ncol(ci50)) {
    sigsi50[[i]] <- wilcox.test(
                   Intensities_50ng[Intensities_50ng$gene == ci50[1,i],col],
                   Intensities_50ng[Intensities_50ng$gene == ci50[2,i],col], exact=FALSE
                 )
    }
    names(sigsi50) <- paste("Group",ci50[1,],"by Group",ci50[2,])

 tests_Intensities_50ng <- data.frame(Test=names(sigsi50),
                    W=unlist(lapply(sigsi50,function(x) x$statistic)),
                    p=unlist(lapply(sigsi50,function(x) x$p.value)),row.names=NULL)

 return(tests_Intensities_50ng)
}


tests_Intensities_50ng <- lapply(colnames(Intensities_50ng)[-1],function(x) test.funi50(Intensities_50ng,x))
names(tests_Intensities_50ng) <- colnames(Intensities_50ng)[-1]
# tests <- do.call(rbind, tests) reprints as data.frame
#KO_list = split(KO_spectral, f = KO_spectral$Gene)


test.funi100 <- function(Intensities_100ng, col) { 

 ci100 <- combn(unique(Intensities_100ng$gene),2)
 sigsi100 <- list()
 for(i in 1:ncol(ci100)) {
    sigsi100[[i]] <- wilcox.test(
                   Intensities_100ng[Intensities_100ng$gene == ci100[1,i],col],
                   Intensities_100ng[Intensities_100ng$gene == ci100[2,i],col], exact=FALSE
                 )
    }
    names(sigsi100) <- paste("Group",ci100[1,],"by Group",ci100[2,])

 tests_Intensities_100ng <- data.frame(Test=names(sigsi100),
                    W=unlist(lapply(sigsi100,function(x) x$statistic)),
                    p=unlist(lapply(sigsi100,function(x) x$p.value)),row.names=NULL)

 return(tests_Intensities_100ng)
}


tests_Intensities_100ng <- lapply(colnames(Intensities_100ng)[-1],function(x) test.funi100(Intensities_100ng,x))
names(tests_Intensities_100ng) <- colnames(Intensities_100ng)[-1]

```

#Writing CSV of the Wilcoxon Test
```{r}
results_Spectral_50ng <- do.call(rbind.data.frame, tests_Spectral_50ng)
write.csv(results_Spectral_50ng,"/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_IsabelasGradientsFirreWTKO//results_50ng_protein_Spectral.csv",row.names = FALSE)
results_Spectral_100ng <- do.call(rbind.data.frame, tests_Spectral_100ng)
write.csv(results_Spectral_100ng,"//scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_IsabelasGradientsFirreWTKO//results_100ng_protein_Spectral.csv",row.names = FALSE)


results_Intensities_50ng <- do.call(rbind.data.frame, tests_Intensities_50ng)
write.csv(results_Intensities_50ng,"/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_IsabelasGradientsFirreWTKO//results_50ng_protein_Intensities.csv",row.names = FALSE)
results_Intensities_100ng <- do.call(rbind.data.frame, tests_Intensities_100ng)
write.csv(results_Intensities_100ng,"/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_IsabelasGradientsFirreWTKO//results_100ng_protein_Intensities.csv",row.names = FALSE)
```

#Histogram of p-values
```{r}
hist(results_Spectral_50ng$p, breaks = 20, main="Frequency of Wilcoxon Rank Sum Test P-values \nComparing KO with WT Mass Spec Spectral Counts from SucGrad F5&6 100ng", xlab = "P-value from Wilcoxon Rank Sum Test", ylab = "Frequency of Genes", labels=TRUE) 
hist(results_Spectral_100ng$p, breaks = 20, main="Frequency of Wilcoxon Rank Sum Test P-values \nComparing KO with WT Mass Spec Spectral Counts from SucGrad F5&6 100ng", xlab = "P-value from Wilcoxon Rank Sum Test", ylab = "Frequency of Genes", labels=TRUE) 

# saving the figure (we will do this over and over again :)
# we will learn ggplot later but we use PDF and turn of null device (plot window) 

pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_IsabelasGradientsFirreWTKO//2022_03_28_Histogram_Wilcoxon_Spectral_50ng_protein_SucGrad_Mar2022.pdf")
hist(results_Spectral_50ng$p, breaks = 20, main="Frequency of Wilcoxon Rank Sum Test P-values \nComparing KO with WT Mass Spec Spectral Counts from SucGrad F5&6 50ng Protein", xlab = "P-value from Wilcoxon Rank Sum Test", ylab = "Frequency of Genes", labels=TRUE) 
dev.off()

pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_IsabelasGradientsFirreWTKO//2022_03_28_Histogram_Wilcoxon_Spectral_100ng_protein_SucGrad_Mar2022.pdf")
hist(results_Spectral_100ng$p, breaks = 20, main="Frequency of Wilcoxon Rank Sum Test P-values \nComparing KO with WT Mass Spec Spectral Counts from SucGrad F5&6 100ng Protein", xlab = "P-value from Wilcoxon Rank Sum Test", ylab = "Frequency of Genes", labels=TRUE) 
dev.off()

#intensities
hist(results_Intensities_50ng$p, breaks = 20, main="Frequency of Wilcoxon Rank Sum Test P-values \nComparing KO with WT Mass Spec Intensities from SucGrad F5&6 50ng Protein", xlab = "P-value from Wilcoxon Rank Sum Test", ylab = "Frequency of Genes", labels=TRUE) 

hist(results_Intensities_100ng$p, breaks = 20, main="Frequency of Wilcoxon Rank Sum Test P-values \nComparing KO with WT Mass Spec Intensities from SucGrad F5&6 100ng Protein", xlab = "P-value from Wilcoxon Rank Sum Test", ylab = "Frequency of Genes", labels=TRUE) 

pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_IsabelasGradientsFirreWTKO//2022_03_28_Histogram_Wilcoxon_Intensities_50ng_protein_SucGrad_Mar2022.pdf")
hist(results_Intensities_50ng$p, breaks = 20, main="Frequency of Wilcoxon Rank Sum Test P-values \nComparing KO with WT Mass Spec Intensitiesl Counts from SucGrad F5&6 50ng Protein", xlab = "P-value from Wilcoxon Rank Sum Test", ylab = "Frequency of Genes", labels=TRUE) 
dev.off()

pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_IsabelasGradientsFirreWTKO//2022_03_28_Histogram_Wilcoxon_Intensities_100ng_protein_SucGrad_Mar2022.pdf")
hist(results_Intensities_100ng$p, breaks = 20, main="Frequency of Wilcoxon Rank Sum Test P-values \nComparing KO with WT Mass Spec Intensitiesl Counts from SucGrad F5&6 100ng Protein", xlab = "P-value from Wilcoxon Rank Sum Test", ylab = "Frequency of Genes", labels=TRUE) 
dev.off()

```

#Genes Below 0.05 and 0.10 p-value
#Feel free to change the names and the pvalue cutoffs
```{r}
results_Spectral_50ng <- results_Spectral_50ng %>% 
  mutate(significance = ifelse(p < 0.05, "very",
                          ifelse(p < 0.10, "significant", "not")))

significant <- c("very", "significant")
pattern_to_search <- paste0(significant, collapse = "|")

significantSpectral_50ng_genes <- results_Spectral_50ng[grepl(pattern_to_search, results_Spectral_50ng$significance), ]

results_Intensities_50ng <- results_Intensities_50ng%>% 
  mutate(significance = ifelse(p < 0.05, "very",
                          ifelse(p < 0.10, "significant", "not")))

significantIntensities_50ng_genes <- results_Intensities_50ng[grepl(pattern_to_search, results_Intensities_50ng$significance), ]

```

##will need to change the gene names below that I put in manually
##make sure genotype entry is the same as above
#Pvalues are on individual graphs, but not the big graph. 
#Graphs here are fancy and pretty close to publication ready. 
#Feel free to change the fill color. It's teal. 
```{r}
#genes with pvalues <0.05. Making Box Whisker Plots, both all together and individual

#Spectral
#in the future I might have to grep these names
sig_genes <- c("anxa1","atp5f1a","btf3","ckb","hdlbp","hnrnpm","mif","naa15","pabpc1","pkp1","rpl10$","rpl38","slc25a5")
pattern_to_search_sig_genes <- paste0(sig_genes, collapse = "|")
long_data_Spectral_sig_genes <- Spectral[, grep(pattern_to_search_sig_genes, colnames(Spectral))]
genotype <- c("WT","WT","WT","WT","WT","WT","WT","WT","WT","WT","KO","KO","KO","KO","KO","KO","KO","KO","KO","KO")
long_data_Spectral_sig_genes <- cbind(genotype,long_data_Spectral_sig_genes)
mm_sigSpectral = melt(long_data_Spectral_sig_genes)

  pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_MassSpec_ChIRP_TVall//2022_03_28_sig_genes_Spectral_boxwhisker_Wilcoxon_S_MassSpec_Mar2022TV_v_Jan2022TV.pdf")
  ggplot(mm_sigSpectral)+geom_boxplot(aes(x=genotype, y=value),fill = "#00AFBB")+facet_grid(.~variable)
  dev.off()


for (var in mm_sigSpectral$variable) { 
 
  pdf(paste("/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_MassSpec_ChIRP_TVall/2022_03_28_MassSpec_SpectralBoxPlots_SignificantGenes//", var, "_sig.pdf", sep=""))
  print(ggpaired(mm_sigSpectral[mm_sigSpectral$variable==var,],x="genotype",y="value",fill="#00AFBB",line.color ="gray")+ggtitle(var)+stat_compare_means(label.x = 0.5))
  dev.off()
  }

#Intensities
long_data_Intensities_sig_genes <- Intensities[, grep(pattern_to_search_sig_genes, colnames(Intensities))]
genotype <- c("WT","WT","WT","WT","WT","WT","WT","WT","WT","WT","KO","KO","KO","KO","KO","KO","KO","KO","KO","KO")
long_data_Intensities_sig_genes <- cbind(genotype,long_data_Intensities_sig_genes)
mm_sigIntensities = melt(long_data_Intensities_sig_genes)

pdf("/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_MassSpec_ChIRP_TVall//2022_03_28_sig_genes_Intensities_boxwhisker_Wilcoxon_MassSpec_Mar2022TV_v_Jan2022TV.pdf")
ggplot(mm_sigIntensities)+geom_boxplot(aes(x=genotype, y=value),fill = "#00AFBB")+facet_grid(.~variable)
dev.off()

for (var in mm_sigIntensities$variable) { 
             
  pdf(paste("/scratch/Shares/rinn/tenaya/ChChCh/2022_03_28_MassSpec_ChIRP_TVall/2022_03_28_MassSpec_IntensitiesBoxPlots_SignificantGenes//", var, "_sig.pdf", sep=""))
  #print(ggplot(mm_sigIntensities[mm_sigIntensities$variable==var,])+geom_boxplot(aes(x=genotype, y=value),fill="#00AFBB")+ggtitle(var))
  print(ggpaired(mm_sigIntensities[mm_sigIntensities$variable==var,],x="genotype",y="value",fill="#00AFBB",line.color ="gray")+ggtitle(var)+stat_compare_means(label.x = 0.5))
  dev.off()
}

#Trying to add pvalues to plots.
#Help websites
#https://www.datanovia.com/en/blog/ggpubr-how-to-add-p-values-generated-elsewhere-to-a-ggplot/
#https://www.r-bloggers.com/2017/06/add-p-values-and-significance-levels-to-ggplots/
#http://www.sthda.com/english/articles/24-ggpubr-publication-ready-plots/76-add-p-values-and-significance-levels-to-ggplots/
```

##Then comes histograms of the spectral and intensities counts
##Also more fancy box plots of the very interesting genes